Chatbots and messaging platforms in the classroom: an analysis from the teacher's perspective

### 2023-01-06 edubots_surveys.Rnw
fix grammar and typos - Introduction p5-6

Initially, a single survey was developed for this purpose and responses from 300
higher education teachers were collected and analysed\textcolor{black}{; this will be explained more fully in the methodology section}. The responses' analysis
entailed the creation of a second survey to which 200 teachers' responses were
collected\textcolor{black}{, with the methodology and collective characteristics that will be explained below. The questions of the second survey focused on discussing teachers'
needs, opinions and preferences of the development of future technology-enhanced
tools and its potential impact on educational institutions’ policies. In order to assess these, this paper investigated the following research questions}:

\begin{itemize}
\item RQ1 - Do teachers use now or want to use messaging apps in their classes?
\item RQ2 - Which chatbots' features would teachers find useful for this purpose?
\item RQ3 - Which kind of interaction do teachers prefer with their students?
\item RQ4 - What kind of interaction media features do teachers value the most?
\end{itemize}

>>>>

Initially, a single survey was developed for this purpose and responses from 300
higher education teachers were collected and analysed\textcolor{black}{; this will be detailed in Section \ref{sec:meth}}. The responses' analysis
led to the preparation of a second survey for teachers and 200 responses were
collected\textcolor{black}{, again following the methodology that will be explained later. The questions of the second survey focused on asking about teachers'
needs, opinions and preferences of the development of future technology-enhanced
tools and its potential impact on educational institutions policies. In order to assess these, this paper layed out the following research questions}:

\begin{itemize}
\item RQ1 - Do teachers use now or want to use messaging apps in their classes?
\item RQ2 - Which chatbots' features would teachers find useful for this purpose?
\item RQ3 - Which kind of interaction do teachers prefer with their students?
\item RQ4 - Which kind of interaction media features do teachers value the most?
\end{itemize}
